The Astropy Project

### 2017-11-21 main.tex
Minor wording changes

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits. We can divide up the commits by
contributor and construct a distribution which is the number of commits
for each contributor versus the rank of the contributor (where 1 is the
contributor who has made the most commits, 2 is the contributor with the
second most commits, and so on). When doing this, we find that this distribution
follows an approximate power-law (with log-slope of
$\approx -0.5$), meaning most of the commits were and are contributed by a
relatively small fraction of the contributor pool.
Roughly half of the commits were contributed by the top $4$
contributors, while $\sim 90$ percent of the commits came from the top $24$
contributors.

>>>>

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits. We can divide up the commits by
contributor and construct a distribution of the number of commits
per contributor ordered by decreasing number of commits. When doing this,
we find that this distribution
follows an approximate power-law (with log-slope of
$\approx -0.5$), meaning most of the commits were and are contributed by a
relatively small fraction of the contributor pool.
Roughly half of the commits were contributed by the top $4$
contributors, while $\sim 90$ percent of the commits came from the top $24$
contributors.
